### 2016-06-20 README.Rmd
Fix `check` warnings and notes
Update to use hurricaneexposuredata package

```{r echo = FALSE}
library(hurricaneexposure)
```

@@

The package currently exists in [a development version](https://github.com/geanders/hurricaneexposure) on GitHub. You can use the following code to load it:

```{r eval = FALSE}
library(devtools)
install_github("geanders/hurricaneexposure", 
               build_vignettes = TRUE)
library(hurricaneexposure)
```

@@

```{r fig.width = 6.5, fig.height = 4}
map_4 <- map_tracks(storms = "Floyd-1999")
map_4
```

>>>>

```{r echo = FALSE, message = FALSE, warning = FALSE}
# If you need to install the hurricaneexposuredata package: 
# library(devtools)
# install_github("geanders/hurricaneexposuredata")
library(hurricaneexposuredata)
library(hurricaneexposure)
```

@@

The package currently exists in [a development version](https://github.com/geanders/hurricaneexposure) on GitHub, and all the associated data is in its own [development version package](https://github.com/geanders/hurricaneexposuredata), also on GitHub. You can use the following code to load both:

```{r eval = FALSE}
library(devtools)
install_github("geanders/hurricaneexposuredata")
install_github("geanders/hurricaneexposure", 
               build_vignettes = TRUE)
library(hurricaneexposuredata)
library(hurricaneexposure)
```

@@

```{r fig.width = 5.5, fig.height = 4}
map_4 <- map_tracks(storms = "Floyd-1999")
map_4
```
